Variance in scarid grazing behavior across Caribbean reef sites

### 2019-09-24 r/Ch2 outline_V3.Rmd
updating stats

```{r, echo=F, message=F, warning=F}
library(here)
library(tidyverse)
library(ggplot2)
library(gridExtra)
library(grid)
library(ggfortify)
library(ggsignif) # boxplot stats
library(EnvStats) # boxplot stats
library(mgcv)
library(MuMIn)
library(knitr)

sum_site <- read.csv(here("data","sum_site.csv"), stringsAsFactors=F) %>%
  select(-X) %>% 
  mutate(island = factor(island, levels = c("Bonaire","Antigua","Barbuda"))) %>%
  arrange(island)
sum_id <- read.csv(here("data","sum_id.csv"), stringsAsFactors=F) %>%
  select(-X) %>% 
  filter(species_code %in% c("stop","qup")) %>%
  mutate(island = factor(island, levels = c("Bonaire","Antigua","Barbuda"))) %>%
  arrange(island) %>%
  filter(fr <= 3000)

### data subset: excluding sites with low sample sizes, including only individuals 15-35 cm
sum_id_sub <- sum_id %>%
  filter(phase == "i" & length_cm >= 15 & length_cm <= 35 & !(species_code == "stop" & site == "Pallaster West") & !(species_code == "qup" & site %in% c("Pallaster East","Rendezvous","Turtle Bay")))

sum_ssp_sub <- sum_id_sub %>% 
  group_by(species, species_code, site, island) %>%
  summarize(
    n=n(),
    length_mean=mean(length_cm),
    length_se=sd(length_cm)/sqrt(n),
    g_frac_mean=mean(g_frac),
    g_frac_median=median(g_frac),
    g_frac_se=sd(g_frac)/sqrt(n),
    br_mean=mean(br,na.rm=TRUE),
    br_median=median(br,na.rm=TRUE),
    br_se=sd(br,na.rm=TRUE)/sqrt(n),
    fr_mean=mean(fr),
    fr_median=median(fr),
    fr_se=sd(fr)/sqrt(n),
    for_dur_mean=mean(for_dur,na.rm=TRUE),
    for_dur_median=median(for_dur,na.rm=TRUE),
    for_dur_se=sd(for_dur,na.rm=TRUE)/sqrt(n),
    for_bites_mean=mean(for_bites,na.rm=TRUE),
    for_bites_median=median(for_bites,na.rm=TRUE),
    for_bites_se=sd(for_bites,na.rm=TRUE)/sqrt(n)
    )

@@

## Figuring out sample sizes/site consolidations...

```{r}
sample_exp <- sum_id %>% 
  filter(phase == "i" & length_cm >= 15 & length_cm <= 35) %>%
  group_by(species, species_code, site, island) %>%
  summarize(
    n=n())

ggplot(filter(sum_id, 
              phase=="i" & length_cm >= 15 & length_cm <= 50 & species_code!="rbp"), 
       aes(factor(site), fr)) + 
  geom_violin(aes(fill=island)) +
  geom_boxplot(width=0.1) + 
  labs(y = "Feeding Rate (bites/hr)", x = "", title = "Hourly feeding rates (i. phase)") +
  geom_signif(comparisons = list(c("Antigua", "Barbuda"),c("Antigua","Bonaire"),c("Barbuda","Bonaire")), map_signif_level=TRUE) +
  facet_grid(.~species) + 
  stat_n_text(angle = 90) +
  scale_fill_brewer(palette="Blues") +
  theme_bw() +
  theme(strip.text = element_text(face = "italic")) +
  theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 90, hjust = 1)) 
```

@@

## 
```{r, eval = F, echo=F, message=F, warning=F}
ggplot(filter(sum_ssp, species_code != "rbp" & phase == "i"), aes(x=factor(site, levels = sum_site$site), y=fr_mean)) +
    geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
    geom_errorbar(aes(ymin=fr_mean-fr_se, ymax=fr_mean+fr_se), width=.2,
                 position=position_dodge(.9)) +
    facet_grid(~species) +
    scale_fill_brewer(palette = "Blues") +
    labs(title="Mean feeding rates of individuals (initial phase)", 
         y="Feeding rate (bites/min)", 
         x="Site") +
    theme_bw() +
    theme(strip.text = element_text(face = "italic"), 
          axis.text.x = element_text(angle = 90, hjust = 1), 
          plot.title = element_text(hjust = 0.5))
```

```{r, echo = F, message = F, warning = F}
# Panel graph of site differences

 # published feeding rate (bites/min) for reference lines if needed
ref_qup15 <- (3329-33*15)/60
ref_qup30 <- (3329-33*30)/60
ref_stop15 <- (1089-17*15-56)/60
ref_stop30 <- (1089-17*30-56)/60

fr_qup <- 
  ggplot(filter(sum_ssp, species_code == "qup" & phase == "i"), 
         aes(x=factor(site, levels = sum_site$site), y=fr_mean)) +
  geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
  geom_errorbar(aes(ymin=fr_mean-fr_se, ymax=fr_mean+fr_se), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_brewer(palette = "Blues") +
  #geom_abline(slope=0, intercept=ref_qup15,  col = "red",lty=2) +
  #geom_abline(slope=0, intercept=ref_qup25,  col = "red",lty=2) +
  #ylim(0, 50) +
  labs(y = "Feeding rate \n (bites/min)", 
       title = "S. vetula") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5, face = "italic"),
        plot.margin = margin(5, 0, 0, 5, unit = "pt"),
        strip.text = element_text(face = "italic"), 
        axis.text.x=element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=8),
        legend.position = "none")

fr_stop <- 
  ggplot(filter(sum_ssp, species_code == "stop" & phase == "i"), 
         aes(x=factor(site, levels = sum_site$site), y=fr_mean)) +
  geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
  geom_errorbar(aes(ymin=fr_mean-fr_se, ymax=fr_mean+fr_se), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_brewer(palette = "Blues") +
  #geom_abline(slope=0, intercept=ref_stop15,  col = "red",lty=2) +
  #geom_abline(slope=0, intercept=ref_stop25,  col = "red",lty=2) +
  labs(y = "",
       # y = "S. vetula \nFeeding rate (bites/hr)", 
       title = "S. viride") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5, face = "italic"),
        plot.margin = margin(5, 4, 0, 0, unit = "pt"),
        strip.text = element_text(face = "italic"), 
        axis.text.x=element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none")

br_qup <- 
  ggplot(filter(sum_ssp, species_code == "qup" & phase == "i"), 
         aes(x=factor(site, levels = sum_site$site), y=br_mean)) +
  geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
  geom_errorbar(aes(ymin=br_mean-br_se, ymax=br_mean+br_se), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_brewer(palette = "Blues") +
  labs(y = "Bite rate \n(bites/sec)", 
       x = "", 
       title = "") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5),
        plot.margin = margin(0, 0, 0, 5, unit = "pt"),
        strip.text = element_text(face = "italic"), 
        axis.text.x=element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=8),
        legend.position = "none")

br_stop <- 
  ggplot(filter(sum_ssp, species_code == "stop" & phase == "i"), 
         aes(x=factor(site, levels = sum_site$site), y=br_mean)) +
  geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
  geom_errorbar(aes(ymin=br_mean-br_se, ymax=br_mean+br_se), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_brewer(palette = "Blues") +
  labs(y = "",
       # y = "S. vetula \nFeeding rate (bites/hr)", 
       x = "", 
       title = "") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5),
        plot.margin = margin(0, 4, 0, 0, unit = "pt"),
        strip.text = element_text(face = "italic"), 
        axis.text.x=element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none")

gfrac_qup <- 
  ggplot(filter(sum_ssp, species_code == "qup" & phase == "i"), 
         aes(x=factor(site, levels = sum_site$site), y=g_frac_mean)) +
  geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
  geom_errorbar(aes(ymin=g_frac_mean-g_frac_se, ymax=g_frac_mean+g_frac_se), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_brewer(palette = "Blues") +
  labs(y = "Time grazing \n(fraction)", 
       x = "", 
       title = "") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5),
        plot.margin = margin(0, 0, 0, 5, unit = "pt"),
        strip.text = element_text(face = "italic"), 
        axis.text.x=element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=8),
        legend.position = "none")

gfrac_stop <- 
  ggplot(filter(sum_ssp, species_code == "stop" & phase == "i"), 
         aes(x=factor(site, levels = sum_site$site), y=g_frac_mean)) +
  geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
  geom_errorbar(aes(ymin=g_frac_mean-g_frac_se, ymax=g_frac_mean+g_frac_se), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_brewer(palette = "Blues") +
  labs(y = "",
       x = "", 
       title = "") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5),
        plot.margin = margin(0, 4, 0, 0, unit = "pt"),
        strip.text = element_text(face = "italic"), 
        axis.text.x=element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none")

fi_qup <- 
  ggplot(filter(sum_ssp, species_code == "qup" & phase == "i"), 
         aes(x=factor(site, levels = sum_site$site), y=for_bites_mean)) +
  geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
  geom_errorbar(aes(ymin=for_bites_mean-for_bites_se, ymax=for_bites_mean+for_bites_se), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_brewer(palette = "Blues") +
  labs(y = "Foray length\n(bites/foray)", 
       x = "", 
       title = "") +
  theme_bw() + 
  theme(plot.margin = margin(0, 0, 0, 5, unit = "pt"),
        axis.title.y = element_text(size=8),
        axis.text.x = element_text(angle = 45, hjust = 1, size=7),
        legend.position = "none")

fi_stop <- 
  ggplot(filter(sum_ssp, species_code == "stop" & phase == "i"), 
         aes(x=factor(site, levels = sum_site$site), y=for_bites_mean)) +
  geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
  geom_errorbar(aes(ymin=for_bites_mean-for_bites_se, ymax=for_bites_mean+for_bites_se), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_brewer(palette = "Blues") +
  labs(y = "",
       x = "", 
       title = "") +
  theme_bw() + 
  theme(plot.margin = margin(0, 4, 0, 0, unit = "pt"),
        axis.text.x = element_text(angle = 45, hjust = 1, size=7),
        legend.position = "none")

legend_plot <- 
  ggplot(filter(sum_ssp, species_code == "stop" & phase == "i"), 
         aes(x=factor(site, levels = sum_site$site), y=g_frac_mean)) +
  geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
  scale_fill_brewer(palette = "Blues") +
  labs(y = "",
       x = "", 
       title = "") +
  theme_bw() +
  theme(legend.position = "right",
        legend.title = element_blank())

@@

grid.arrange(
  arrangeGrob(fr_qup, fr_stop, gfrac_qup, gfrac_stop, br_qup, br_stop, fi_qup, fi_stop, ncol=2, heights = c(1.5,1.5,1.5,3)), 
              arrangeGrob(legend), 
              ncol=2, widths = c(5,1))

@@

The variations in grazing behaviors demonstrated here may be driven by several potential underlying mechanisms. Figure 3 shows the relationships between various reef characteristics and scarid feeding rate. Because study sites expectedly varied across a number of interrelated fish and benthic dimensions (PCA - appendix?), it is impossible to conclusively establish any explicit mechanisms here. Instead I present several hypotheses that may be driving these observed behavioral trends and discuss evidence for and implications of each.

```{r, echo=F, message=F, warning=F}
fr_q1 <- ggplot(filter(sum_ssp, species_code == "qup" & phase == "i"), aes(x = scar_bm/1000, y = fr_mean)) +
  geom_smooth(method="loess", span=1) +
  geom_point(shape=18) +
  ylim(-10, 60) +
  labs(y = "",
       title = "") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5),
        plot.margin = margin(0, 1, 0, 0, unit = "pt"),
        axis.text.x = element_blank(),
        axis.title.x = element_blank()
        )

fr_q2 <- ggplot(filter(sum_ssp, species_code == "qup" & phase == "i"), aes(x = consp_den, y = fr_mean)) +
  geom_smooth(method="loess", span=1) +
  geom_point(shape=18) +
  ylim(-10, 60) +
  labs(y = "", 
       title = "") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        plot.margin = margin(0, 1, 0, 1, unit = "pt"),
        axis.text.x = element_blank(),
        axis.title.x = element_blank()
        )

fr_q3 <- ggplot(filter(sum_ssp, species_code == "qup" & phase == "i"), aes(x = rugosity, y = fr_mean)) +
  geom_smooth(method="loess", span=1) +
  geom_point(shape=18) +
  ylim(-10, 60) +
  labs(y = "", 
       title = "") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        plot.margin = margin(0, 1, 0, 1, unit = "pt"),
        axis.text.x = element_blank(),
        axis.title.x = element_blank()
        )

fr_q4 <- ggplot(filter(sum_ssp, species_code == "qup" & phase == "i"), aes(x = ta_canopy, y = fr_mean)) +
  geom_smooth(method="loess", span=1) +
  geom_point(shape=18) +
  ylim(-10, 60) +
  labs(y = "", 
       title = "") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        plot.margin = margin(0, 1, 0, 1, unit = "pt"),
        axis.text.x = element_blank(),
        axis.title.x = element_blank()
        )

fr_q5 <- ggplot(filter(sum_ssp, species_code == "qup" & phase == "i"), aes(x = ta_cover, y = fr_mean)) +
  geom_smooth(method="loess", span=1) +
  geom_point(shape=18) +
  ylim(-10, 60) +
  labs(y = "",
       title = "") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        plot.margin = margin(0, 1, 0, 1, unit = "pt"),
        axis.text.x = element_blank(),
        axis.title.x = element_blank()
        )

fr_q7 <- ggplot(filter(sum_ssp, species_code == "qup" & phase == "i"), aes(x = ma_cover, y = fr_mean)) +
  geom_smooth(method="loess", span=1) +
  geom_point(shape=18) +
  ylim(-10, 60) +
  labs(y = "", 
       title = "") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        plot.margin = margin(0, 1, 0, 1, unit = "pt"),
        axis.text.x = element_blank(),
        axis.title.x = element_blank()
        )

fr_s1 <- ggplot(filter(sum_ssp, species_code == "stop" & phase == "i"), aes(x = scar_bm/1000, y = fr_mean)) +
  geom_smooth(method="loess", span=1) +
  geom_point(shape=18) +
  ylim(-5, 20) +
  labs(y = "",
       x = expression(atop(NA, atop(textstyle('Scarid biomass'),
                               textstyle('(kg/100m'^2*')')))),
       title = "") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5),
        plot.margin = margin(0, 1, 0, 0, unit = "pt"),
        axis.title.x = element_text(size = 9)
        )

fr_s2 <- ggplot(filter(sum_ssp, species_code == "stop" & phase == "i"), aes(x = consp_den, y = fr_mean)) +
  geom_smooth(method="loess", span=1) +
  geom_point(shape=18) +
  ylim(-5, 20) +
  labs(y = "", 
       x = expression(atop(NA, atop(textstyle('Conspec. density'),
                               textstyle('(indv/100m'^2*')')))),
       title = "") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_text(size = 9),
        plot.margin = margin(0, 1, 0, 1, unit = "pt")
        )

fr_s3 <- ggplot(filter(sum_ssp, species_code == "stop" & phase == "i"), aes(x = rugosity, y = fr_mean)) +
  geom_smooth(method="loess", span=1) +
  geom_point(shape=18) +
  ylim(-5, 20) +
  labs(y = "", 
       x = expression(atop(NA, atop(textstyle('Rugosity'),
                               textstyle('  ')))), 
       title = "") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_text(size = 9),
        plot.margin = margin(0, 1, 0, 1, unit = "pt")
        )

>>>>

```{r, echo=F, message=F, warning=F}
library(here)
library(tidyverse)
library(R.utils)
library(ggplot2)
library(gridExtra)
library(grid)
library(ggfortify)
library(ggsignif) # boxplot stats
library(EnvStats) # boxplot stats
library(mgcv)
library(MuMIn)
library(knitr)

site <- read.csv(here("data", "site.csv"), strip.white = T, stringsAsFactors = F) %>% select(-X)
sum_id <- read.csv(here("data","sum_id.csv"), stringsAsFactors=F) %>%
  select(-X) %>% 
  filter(phase == "i" & 
           species_code %in% c("stop","qup") & 
           length_cm <= 30 & length_cm >= 15 & 
           !(species_code == "stop" & site == "Pallaster West") & 
           !(species_code == "qup" & site %in% c("Pallaster East","Rendezvous","Turtle Bay"))) %>%
  mutate(island = factor(island, levels = c("Bonaire","Antigua","Barbuda"))) %>%
  arrange(island) %>%
  filter(fr <= 3000)

sum_ssp_sub <- sum_id %>% 
  group_by(species, species_code, site, island) %>%
  summarize(
    n=n(),
    length_median=median(length_cm),
    length_se=sd(length_cm)/sqrt(n),
    g_frac_median=median(g_frac),
    g_frac_median=median(g_frac),
    g_frac_se=sd(g_frac)/sqrt(n),
    br_median=median(br,na.rm=TRUE),
    br_median=median(br,na.rm=TRUE),
    br_se=sd(br,na.rm=TRUE)/sqrt(n),
    fr_median=median(fr),
    fr_median=median(fr),
    fr_se=sd(fr)/sqrt(n),
    for_dur_median=median(for_dur,na.rm=TRUE),
    for_dur_median=median(for_dur,na.rm=TRUE),
    for_dur_se=sd(for_dur,na.rm=TRUE)/sqrt(n),
    for_bites_median=median(for_bites,na.rm=TRUE),
    for_bites_median=median(for_bites,na.rm=TRUE),
    for_bites_se=sd(for_bites,na.rm=TRUE)/sqrt(n)
    ) %>%
  left_join(site, by = c("island","site"))

@@

## Sample sizes (Table S1)
```{r}
sample <- sum_id %>%
  group_by(island, site, species) %>% 
  summarize(n=n()) %>%
  arrange(island) %>%
  rename_all(capitalize)
kable(sample)
write.csv(sample, file = here("figs/sample.csv"))

sample_vir_sum <- sum_id %>% 
  filter(species_code == "stop") %>% 
  group_by(site, species, island) %>% 
  summarize(n=n()) %>%
  group_by(species) %>% 
  summarize(n_sites = n(),
            n_total = sum(n),
            n_median = median(n),
            se = sd(n)/sqrt(n_sites))

sample_vet_sum <- sum_id %>% 
  filter(species_code == "qup") %>% 
  group_by(site, species, island) %>% 
  summarize(n=n()) %>%
  group_by(species) %>% 
  summarize(n_sites = n(),
            n_total = sum(n),
            n_median = median(n),
            se = sd(n)/sqrt(n_sites))

@@

## Testing parametric assumptions
```{r}
### Normality

hist(sum_id$fr) # positive skew
shapiro.test(sum_id$fr) # non-normal

hist(sum_id$br) # positive skew
shapiro.test(sum_id$br) # non-normal

hist(sum_id$g_frac) # positive skew
shapiro.test(sum_id$g_frac) # non-normal

hist(sum_id$for_bites) # positive skew
shapiro.test(sum_id$for_bites) # non-normal

# all positively skewed, non-normally distributed -> should use median, should use Kruskall-Wallis
```

## Panel graph of site differences
```{r, echo = F, message = F, warning = F}
# published feeding rate (bites/min) for reference lines if needed
ref_qup15 <- (3329-33*15)/60
ref_qup30 <- (3329-33*30)/60
ref_stop15 <- (1089-17*15-56)/60
ref_stop30 <- (1089-17*30-56)/60

fr_qup <- 
  ggplot(filter(sum_ssp_sub, species_code == "qup"), 
         aes(x=factor(site, levels = sum_site$site), y=fr_median)) +
  geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
  geom_errorbar(aes(ymin=fr_median-fr_se, ymax=fr_median+fr_se), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_brewer(palette = "Blues") +
  #geom_abline(slope=0, intercept=ref_qup15,  col = "red",lty=2) +
  #geom_abline(slope=0, intercept=ref_qup25,  col = "red",lty=2) +
  #ylim(0, 50) +
  labs(y = "Grazing rate \n (bites/min)", 
       title = "S. vetula") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5, face = "italic"),
        plot.margin = margin(5, 0, 0, 5, unit = "pt"),
        strip.text = element_text(face = "italic"), 
        axis.text.x=element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=8),
        legend.position = "none")

fr_stop <- 
  ggplot(filter(sum_ssp_sub, species_code == "stop"), 
         aes(x=factor(site, levels = sum_site$site), y=fr_median)) +
  geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
  geom_errorbar(aes(ymin=fr_median-fr_se, ymax=fr_median+fr_se), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_brewer(palette = "Blues") +
  #geom_abline(slope=0, intercept=ref_stop15,  col = "red",lty=2) +
  #geom_abline(slope=0, intercept=ref_stop25,  col = "red",lty=2) +
  labs(y = "",
       # y = "S. vetula \nFeeding rate (bites/hr)", 
       title = "S. viride") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5, face = "italic"),
        plot.margin = margin(5, 4, 0, 0, unit = "pt"),
        strip.text = element_text(face = "italic"), 
        axis.text.x=element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none")

br_qup <- 
  ggplot(filter(sum_ssp_sub, species_code == "qup"), 
         aes(x=factor(site, levels = sum_site$site), y=br_median)) +
  geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
  geom_errorbar(aes(ymin=br_median-br_se, ymax=br_median+br_se), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_brewer(palette = "Blues") +
  labs(y = "Bite rate \n(bites/sec)", 
       x = "", 
       title = "") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5),
        plot.margin = margin(0, 0, 0, 5, unit = "pt"),
        strip.text = element_text(face = "italic"), 
        axis.text.x=element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=8),
        legend.position = "none")

br_stop <- 
  ggplot(filter(sum_ssp_sub, species_code == "stop"), 
         aes(x=factor(site, levels = sum_site$site), y=br_median)) +
  geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
  geom_errorbar(aes(ymin=br_median-br_se, ymax=br_median+br_se), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_brewer(palette = "Blues") +
  labs(y = "",
       # y = "S. vetula \nFeeding rate (bites/hr)", 
       x = "", 
       title = "") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5),
        plot.margin = margin(0, 4, 0, 0, unit = "pt"),
        strip.text = element_text(face = "italic"), 
        axis.text.x=element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none")

gfrac_qup <- 
  ggplot(filter(sum_ssp_sub, species_code == "qup"), 
         aes(x=factor(site, levels = sum_site$site), y=g_frac_median)) +
  geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
  geom_errorbar(aes(ymin=g_frac_median-g_frac_se, ymax=g_frac_median+g_frac_se), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_brewer(palette = "Blues") +
  labs(y = "Time grazing \n(fraction)", 
       x = "", 
       title = "") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5),
        plot.margin = margin(0, 0, 0, 5, unit = "pt"),
        strip.text = element_text(face = "italic"), 
        axis.text.x=element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=8),
        legend.position = "none")

gfrac_stop <- 
  ggplot(filter(sum_ssp_sub, species_code == "stop"), 
         aes(x=factor(site, levels = sum_site$site), y=g_frac_median)) +
  geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
  geom_errorbar(aes(ymin=g_frac_median-g_frac_se, ymax=g_frac_median+g_frac_se), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_brewer(palette = "Blues") +
  labs(y = "",
       x = "", 
       title = "") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5),
        plot.margin = margin(0, 4, 0, 0, unit = "pt"),
        strip.text = element_text(face = "italic"), 
        axis.text.x=element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none")

fi_qup <- 
  ggplot(filter(sum_ssp_sub, species_code == "qup"), 
         aes(x=factor(site, levels = sum_site$site), y=for_bites_median)) +
  geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
  geom_errorbar(aes(ymin=for_bites_median-for_bites_se, ymax=for_bites_median+for_bites_se), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_brewer(palette = "Blues") +
  labs(y = "Grazing intensity\n(bites/foray)", 
       x = "", 
       title = "") +
  theme_bw() + 
  theme(plot.margin = margin(0, 0, 0, 5, unit = "pt"),
        axis.title.y = element_text(size=8),
        axis.text.x = element_text(angle = 45, hjust = 1, size=7),
        legend.position = "none")

fi_stop <- 
  ggplot(filter(sum_ssp_sub, species_code == "stop"), 
         aes(x=factor(site, levels = sum_site$site), y=for_bites_median)) +
  geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
  geom_errorbar(aes(ymin=for_bites_median-for_bites_se, ymax=for_bites_median+for_bites_se), width=.2,
                 position=position_dodge(.9)) +
  scale_fill_brewer(palette = "Blues") +
  labs(y = "",
       x = "", 
       title = "") +
  theme_bw() + 
  theme(plot.margin = margin(0, 4, 0, 0, unit = "pt"),
        axis.text.x = element_text(angle = 45, hjust = 1, size=7),
        legend.position = "none")

legend_plot <- 
  ggplot(filter(sum_ssp, species_code == "stop" & phase == "i"), 
         aes(x=factor(site, levels = sum_site$site), y=g_frac_median)) +
  geom_bar(stat = "identity", aes(fill = island), position = "dodge") +
  scale_fill_brewer(palette = "Blues") +
  labs(y = "",
       x = "", 
       title = "") +
  theme_bw() +
  theme(legend.position = "right",
        legend.title = element_blank())

@@

@@

## Kruskal-Wallis tests
```{r}
vir <- sum_id %>% filter(species_code == "stop")
vet <- sum_id %>% filter(species_code == "qup")

kruskal.test(fr ~ site, data = vet) # p<0.001
kruskal.test(fr ~ site, data = vir) # p<0.001

kruskal.test(br ~ site, data = vet) # p>0.5 (p=0.63)
kruskal.test(br ~ site, data = vir) # p>0.5 (p=0.55)

kruskal.test(g_frac ~ site, data = vet) # p<0.001
kruskal.test(g_frac ~ site, data = vir) # p<0.001

kruskal.test(for_bites ~ site, data = vet) # p<0.001
kruskal.test(for_bites ~ site, data = vir) # p<0.001
```

## Loess plots of various drivers

```{r, echo=F, message=F, warning=F}
fr_q1 <- ggplot(filter(sum_ssp_sub, species_code == "qup"), aes(x = scar_bm/1000, y = fr_median)) +
  geom_smooth(method="loess", span=1) +
  geom_point(shape=18) +
  ylim(-10, 60) +
  labs(y = "",
       title = "") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5),
        plot.margin = margin(0, 1, 0, 0, unit = "pt"),
        axis.text.x = element_blank(),
        axis.title.x = element_blank()
        )

fr_q2 <- ggplot(filter(sum_ssp_sub, species_code == "qup"), aes(x = consp_den, y = fr_median)) +
  geom_smooth(method="loess", span=1) +
  geom_point(shape=18) +
  ylim(-10, 60) +
  labs(y = "", 
       title = "") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        plot.margin = margin(0, 1, 0, 1, unit = "pt"),
        axis.text.x = element_blank(),
        axis.title.x = element_blank()
        )

fr_q3 <- ggplot(filter(sum_ssp_sub, species_code == "qup"), aes(x = rugosity, y = fr_median)) +
  geom_smooth(method="loess", span=1) +
  geom_point(shape=18) +
  ylim(-10, 60) +
  labs(y = "", 
       title = "") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        plot.margin = margin(0, 1, 0, 1, unit = "pt"),
        axis.text.x = element_blank(),
        axis.title.x = element_blank()
        )

fr_q4 <- ggplot(filter(sum_ssp_sub, species_code == "qup"), aes(x = ta_canopy, y = fr_median)) +
  geom_smooth(method="loess", span=1) +
  geom_point(shape=18) +
  ylim(-10, 60) +
  labs(y = "", 
       title = "") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        plot.margin = margin(0, 1, 0, 1, unit = "pt"),
        axis.text.x = element_blank(),
        axis.title.x = element_blank()
        )

fr_q5 <- ggplot(filter(sum_ssp_sub, species_code == "qup"), aes(x = ta_cover, y = fr_median)) +
  geom_smooth(method="loess", span=1) +
  geom_point(shape=18) +
  ylim(-10, 60) +
  labs(y = "",
       title = "") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        plot.margin = margin(0, 1, 0, 1, unit = "pt"),
        axis.text.x = element_blank(),
        axis.title.x = element_blank()
        )

fr_q7 <- ggplot(filter(sum_ssp_sub, species_code == "qup"), aes(x = ma_cover, y = fr_median)) +
  geom_smooth(method="loess", span=1) +
  geom_point(shape=18) +
  ylim(-10, 60) +
  labs(y = "", 
       title = "") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        plot.margin = margin(0, 1, 0, 1, unit = "pt"),
        axis.text.x = element_blank(),
        axis.title.x = element_blank()
        )

fr_s1 <- ggplot(filter(sum_ssp_sub, species_code == "stop"), aes(x = scar_bm/1000, y = fr_median)) +
  geom_smooth(method="loess", span=1) +
  geom_point(shape=18) +
  ylim(-5, 20) +
  labs(y = "",
       x = expression(atop(NA, atop(textstyle('Scarid biomass'),
                               textstyle('(kg/100m'^2*')')))),
       title = "") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5),
        plot.margin = margin(0, 1, 0, 0, unit = "pt"),
        axis.title.x = element_text(size = 9)
        )

fr_s2 <- ggplot(filter(sum_ssp_sub, species_code == "stop"), aes(x = consp_den, y = fr_median)) +
  geom_smooth(method="loess", span=1) +
  geom_point(shape=18) +
  ylim(-5, 20) +
  labs(y = "", 
       x = expression(atop(NA, atop(textstyle('Conspec. density'),
                               textstyle('(indv/100m'^2*')')))),
       title = "") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_text(size = 9),
        plot.margin = margin(0, 1, 0, 1, unit = "pt")
        )

fr_s3 <- ggplot(filter(sum_ssp_sub, species_code == "stop"), aes(x = rugosity, y = fr_median)) +
  geom_smooth(method="loess", span=1) +
  geom_point(shape=18) +
  ylim(-5, 20) +
  labs(y = "", 
       x = expression(atop(NA, atop(textstyle('Rugosity'),
                               textstyle('  ')))), 
       title = "") +
  theme_bw() + 
  theme(plot.title = element_text(hjust = 0.5),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_text(size = 9),
        plot.margin = margin(0, 1, 0, 1, unit = "pt")
        )
